---
title: "dygraphs"
---

# The `dygraphs` package

The [package](http://rstudio.github.io/dygraphs/) and the JavaScript library [website](http://dygraphs.com/).

# A quick example

```{r}
library(dygraphs)

dygraph(nhtemp, main = "New Haven Temperatures") %>% 
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))
```
<br>

# `xts`

Datasets must either be time series data or numeric data. For time series, this must be an `xts` object or an object which is convertible to `xts` (such as `zoo`). For numeric data, this must be a named list or data frame, where the first element/column provides x-axis values and all subsequent elements/columns provide one or more series of y-values.

# Quarterly time series

We use the quarterly time series of the number of Australian residents.

```{r}
head(austres)

library(xts)

# Convert austres into an xts object
au <- as.xts(austres)
head(au, 5)
```

```{r}
library(dygraphs)

dygraph(au, main = "Number of Australian residents") %>% 
  dyRangeSelector(dateWindow = c("1972-01-01", "1990-01-01"))
```
<br>

# Monthly time series

```{r}
head(sunspots)

library(xts)

# Convert sunspots to xts
sunspots_xts <- as.xts(sunspots)
head(sunspots_xts, 5)
```

```{r}
library(dygraphs)

dygraph(sunspots_xts, main = "Sunspots") %>% 
  dyRangeSelector(dateWindow = c("1800-01-01", "1830-01-01"))
```
<br>

# Options

```{r}
lungDeaths <- cbind(ldeaths, mdeaths, fdeaths)

head(lungDeaths, 3)
```

## Colors

```{r}
library(dygraphs)

dygraph(lungDeaths, main = "Deaths from Lung Disease (UK)") %>%
  dyOptions(colors = c('red', 'blue', 'orange'))

dygraph(lungDeaths, main = "Deaths from Lung Disease (UK)") %>%
  dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2"))


```

## Steps, fill (area), points, size, shape

```{r}
library(dygraphs)

# Step plots
dygraph(lungDeaths, main = "Deaths from Lung Disease (UK)") %>%
  dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2")) %>%
  dyOptions(stepPlot = TRUE)
# dyOptions(fillGraph = TRUE, fillAlpha = 0.4)
# dyOptions(drawPoints = TRUE, pointSize = 2)
# dyOptions(drawPoints = TRUE, pointSize = 5, pointShape = "triangle")
# triangle, square, diamond, pentagon, hexagon, circle, star, plus, ex

```

## Mix series

```{r}
library(dygraphs)

dygraph(lungDeaths, main = "Deaths from Lung Disease (UK)") %>%
  dySeries("ldeaths", drawPoints = FALSE, color = "red") %>%
  dySeries("mdeaths", drawPoints = TRUE, color = "blue") %>%
  dySeries("fdeaths", stepPlot = TRUE, fillGraph = TRUE, color = "orange")
# dySeries("ldeaths", strokeWidth = 2, strokePattern = "dashed")
# dyGroup(c("mdeaths", "ldeaths"), drawPoints = TRUE, color = c("blue", "green"))
```

## More parameters and settings

- Series Highlighting.
- Axis Options.
- Labels & legends.
- Time Zones.
- Range Selector.
- Candlestick Charts (Stock Exchanges).
- Synchronization.
- Straw Broom Charts (Stock Exchanges).
- Roll Periods (moving average and smoothing).
- Annotation/Shading.
- Events and Limits.
- Upper and Lower Bars (confidence intervals).
- Plugins (for interactivity).
- Custom Plotters.
- Colored ribbons (for displaying 'regimes').

---