---
title: "Highcharter"
---

# The `highcharter` package

The [package](http://jkunst.com/highcharter/) is free for non-commercial use but requires a license in corporate and government fields. 

We can plot a variety of charts and maps that might not be available with `plotly` and `rbokeh`. More specifically: treemaps, better treatment of time series and stock charts (the related packages and topics such as autocovariance and autocorrelation), survival functions, sparkline charts. The package comes with over 500 themes (The Economist, Financial Times, Google, etc.). We can have motion charts like `plotly`, but also drag points like JavaScript libraries. 

Consult the [demo site](https://www.highcharts.com/demo).

# A quick example

With the `mtcars` dataset.

```{r, include=FALSE}
library(highcharter)

data(diamonds, mpg, package = "ggplot2")
```

```{r}
library(highcharter)

hchart(mpg, "scatter", hcaes(x = displ, y = hwy, group = class))
```

# Time series and forecasts

With the `AirPassengers` dataset.

```{r}
library(forecast)

airforecast <- forecast(auto.arima(AirPassengers), level = 95)

library(highcharter)

hchart(airforecast)
```

Average temperatures in New York City.

```{r}
library(highcharter)
data(citytemp)

hc <- highchart() %>% 
  hc_xAxis(categories = citytemp$month) %>% 
  hc_add_series(name = "New York", data = citytemp$new_york) %>% 
  hc_xAxis(title = list(text = "Month"),
           opposite = TRUE,
           minorTickInterval = "auto",
           minorGridLineDashStyle = "LongDashDotDot",
           plotLines = list(
             list(label = list(text = "Mid-year"),
                  color = "#FF0000",
                  width = 2,
                  value = 6))) %>% 
  hc_xAxis(plotBands = list(
             list(from = 9, to = 12, color = "rgba(100, 0, 0, 0.1)",
                  label = list(text = "This is a plotBand")))) 

hc
```

# Treemaps

A federal government budget: revenues and expenses.

```{r, include=FALSE}
budget <- read.csv('data/CanadaFederalBudget.csv', sep = ';', header = TRUE)
b_revenues <- subset(budget, budget$RevExp == 'Revenue outlook')
b_expenses <- subset(budget, budget$RevExp == 'Program expenses outlook')
```

```{r}
library(highcharter)

hchart(b_revenues, "treemap", hcaes(x = Details, value = Budget2016, color = Budget2016))

hchart(b_expenses, "treemap", hcaes(x = Details, value = -Budget2016, color = -Budget2016))
```

# Stock Exchanges

The CAD/USD exchange rate.

```{r}
suppressPackageStartupMessages(library(quantmod))

x <- getSymbols("CAD/USD", src = "oanda", auto.assign = FALSE)

library(highcharter)

hchart(x)
```

# Survival analysis

Subscriber churn (deactivation rate) in telecom.

```{r, include=FALSE}
telco <- read.csv('data/Telco_Customer_Churn.csv', header = TRUE)
telco$Churn <- as.factor(telco$Churn)

# remove the tenure = 0
summary(telco$tenure)
dim(telco)

telco2 <- subset(telco, telco$tenure != 0)

# convert Churn
levels(telco2$Churn) <- c(0, 1)
telco2$Churn <- as.integer(telco2$Churn)
telco2$Churn <- telco2$Churn - 1
```

```{r}
library(survival)

fit <- survfit(Surv(tenure, Churn) ~ Contract, data = telco2)

library(highcharter)

hchart(fit, ranges = TRUE)
```

```{r}
library(survival)

cox_model <- coxph(Surv(tenure, Churn) ~ Contract,
                   method = 'efron',
                   data = telco2)

fit_cox_model <- survfit(cox_model)

library(highcharter)

hchart(fit_cox_model, ranges = TRUE)
```

# Component analysis

```{r, include=FALSE}
liberty12 <- read.csv('data/liberty12.csv', header = TRUE)
liberty12 <- na.omit(liberty12)
rownames(liberty12) <- liberty12[, 1]
liberty12 <- liberty12[, -1]

fathers <- read.csv2('data/fathers.csv', header = TRUE)
rownames(fathers) <- fathers[, 1]
fathers <- fathers[, -1]
```

Each year, the Heritage Foundation along with the Wall Street Journal releases an Index of Economic Freedom where countries are measured with 12 metrics (12 'freedoms').

Each Freedom metrics are percentages; 100 being the highest value:

1. Property Rights
1. Judicial Effectiveness
1. Government Integrity
1. Tax Burden
1. Government Spending
1. Fiscal Health
1. Business Freedom
1. Labor Freedom
1. Monetary Freedom
1. Trade Freedom
1. Investment Freedom
1. Financial Freedom

```{r}
library(highcharter)

hchart(princomp(liberty12, cor = TRUE))
```

# Splom

With the `mtcars` dataset.

```{r}
library(highcharter)

hchart(cor(mtcars))
```

# Map

A choropleth of North America (region are filled with fake data).


```{r, include=FALSE}
library(dplyr)

mapdata <- get_data_from_map(download_map_data("custom/usa-and-canada"))
glimpse(mapdata)

set.seed(1234)

data_fake <- mapdata %>% 
  select(code = `hc-a2`) %>% 
  mutate(value = 1e5 * abs(rt(nrow(.), df = 10)))

glimpse(data_fake)
```

```{r}
library(highcharter)

hcmap("custom/usa-and-canada", 
      data = data_fake, 
      value = "value",
      joinBy = c("hc-a2", "code"), 
      name = "Fake data",
      dataLabels = list(enabled = TRUE, format = '{point.name}'),
      borderColor = "#FAFAFA", borderWidth = 0.1,
      tooltip = list(valueDecimals = 2, valuePrefix = "$", valueSuffix = " USD")) %>% 
  hc_mapNavigation(enabled = TRUE) %>% 
  hc_exporting(enabled = TRUE)
```

A bubble map with the same fake data.

```{r}
hcmap("custom/usa-and-canada", 
      data = data_fake, 
      type = "mapbubble",
      value = "value",
      joinBy = c("hc-a2", "code"), 
      name = "Fake data",
      dataLabels = list(enabled = TRUE, format = '{point.name}'),
      borderColor = "#FAFAFA", borderWidth = 0.1,
      tooltip = list(valueDecimals = 2, valuePrefix = "$", valueSuffix = " USD")) %>% 
  hc_mapNavigation(enabled = TRUE) 
```

---