---
title: "plotly"
---

# The `plotly` package

Plotly graphing library runs in different languages (Scala, JavaScript, Python, MATLAB). With the R [package](https://plot.ly/r/), we can plot a variety of charts (basic, statistical, scientific, financial, 3D) and maps (with events, choropleths, bubbles, lines, scattermapboxes).

The package runs locally in a web browser or in a RStudio viewer. We can publish charts to the web with Plotly's web service.

- [`plotly` for R master class](https://cpsievert.github.io/plotly_book/plot-ly-for-collaboration.html)
- [RDocumentation](https://www.rdocumentation.org/packages/plotly/versions/4.5.2?).
- The [gallery](https://plot.ly/r/).

# Scatter charts

With the `diamonds` dataset.

```{r}
suppressPackageStartupMessages(library(plotly))

# The diamonds dataset
head(diamonds, 3)

plot_ly(diamonds, x = ~carat, y = ~price, color = ~carat, size = ~carat)
```

## Scatter vs. 2D histogram plots

This an dataset about 753 working women. 428 work outside the home, 325 don't. We remove observations where `hours` is zero. We also have socioeconomic factors affecting the work decision.

The scatter plot only.

```{r, include=FALSE}
library(readxl)

# Read in the data set and assign to the object
work <- read_excel('data/Survival.xls', sheet = 'work')
str(work)
work$largecity <- as.factor(work$largecity)
work <- subset(work, work$hours != 0)
```

```{r}
plot_ly(work, x = ~faminc, y = ~hours, color = ~largecity, size = ~exper)
```

The scatter plot vs. the 2D histogram plot.

```{r}
p <- plot_ly(work, x = ~faminc, y = ~hours)

pp <- subplot(
  p %>% add_markers(alpha = 0.2),
  p %>% add_histogram2d()
)

pp
```

# Bar charts

With the `diamonds` dataset.

```{r, include=FALSE}
library(dplyr)

# Calculate the numbers of diamonds for each cut-clarity combination
diamonds_bucket <- diamonds %>% 
  count(cut, clarity)
```

```{r}
plot_ly(diamonds_bucket, x = ~cut, y = ~n, color = ~clarity, type = "bar")
```

# Box plots

Create box plots that are grouped, colored, and that display the underlying data distribution.

```{r}
# The non fancy box plot
plot_ly(y = ~rnorm(50), type = "box")
```

```{r, eval=TRUE}
# The fancy box plot
plot_ly(diamonds, y = ~price, color = ~cut, type = 'box')
```

```{r, eval=TRUE}
# The super fancy box plot
plot_ly(diamonds, x = ~cut, y = ~price, color = ~clarity, type = 'box') %>%
  layout(boxmode = "group")
```

# Getting fancy with charts

## Visualizing volcano data

Mount Eden is a volcano in the Auckland volcanic field. The `volcano` dataset gives topographic information for Mount Eden on a 10m by 10m grid.

One way to look at the topographic data is via a heatmap. The heatmap's color pattern visualizes how the height of the volcano's surface fluctuates within this 10m by 10m grid.

Alternatively, we could visualize the data by making a 3D surface plot.

```{r, include=FALSE}
# The volcano data
str(volcano)
```

```{r}
# The heatmap
plot_ly(z = ~volcano, type = 'heatmap')

# The 3D surface map
plot_ly(z = ~volcano, type = 'surface')
```

## Interactive `ggplot2`

Convert the `ggplot2` into interactive versions; see [examples](https://plot.ly/ggplot2/).

```{r, eval=TRUE}
library(ggplot2)

# Create the ggplot2 graph
ggplot(mtcars, aes(x = wt, y = mpg, col = cyl)) +
  geom_point()

# Make the plot interactive
ggplotly()
```

```{r}
# Or...
ggplotly( ggplot(mtcars, aes(x = wt, y = mpg, col = cyl)) +
  geom_point() )
```

## Sliding into another example

Visualize the decease on the US roads. Use the 'sliders' to modify the chart.

```{r, eval=FALSE, include=FALSE}
# Set the working directory to upload the data
getwd()
setwd("/home/ugo/Documents/Rprojects/rmarkdown")
```

```{r, include=FALSE}
USAccDeaths <- read.csv('data/USAccDeaths.csv')
#USAccDeaths$date <- as.POSIXct(USAccDeaths$date)
str(USAccDeaths)
```

```{r, eval=TRUE}
# Monthly totals of accidental deaths in the USA
plot_ly(x = ~USAccDeaths$date, y = ~USAccDeaths$deaths) %>% 
  add_lines() %>%
  rangeslider()
```

Implement a range slider to a stock graph.

```{r, include=FALSE}
apple_stock_price <- read.csv('data/apple_stock_price.csv')
#USAccDeaths$Date <- as.POSIXct(USAccDeaths$Date)
str(apple_stock_price)
```

```{r, eval=TRUE}
# Apple Stock Price With Rangeslider
plot_ly(apple_stock_price, x = ~Date) %>%
  add_lines(y = ~AAPL.Adjusted, name = "Apple") %>% 
  rangeslider() %>% 
  layout(
    title = "Stock Price Apple",
    xaxis = list(title = "Date"),
    yaxis = list(title = "Price"))
```

# Maps

## Interactive US airports

A map provides an easy way to visualize how a measurement varies across a geographic area or the level of variability within a region.

```{r, include=FALSE}
library(readr)

# 1
airport_traffic <- read_csv('data/airport_traffic.csv')
airport_traffic$no <- NULL
airport_traffic$iata <- as.factor(airport_traffic$iata)
airport_traffic$airport <- as.factor(airport_traffic$airport)
airport_traffic$city <- as.factor(airport_traffic$city)
airport_traffic$state <- as.factor(airport_traffic$state)
airport_traffic$country <- as.factor(airport_traffic$country)

# 2
airports <- read_csv('data/airports.csv')
airports$Timezone <- as.integer(airports$Timezone)
airports$DST <- as.factor(airports$DST)

str(airport_traffic)
str(airports)
```

```{r, eval=TRUE}
# Most Trafficked US Airports
g <- list(
  scope = 'usa',
  showland = TRUE,
  landcolor = toRGB("gray95")
)

plot_geo(airport_traffic, lat = ~lat, lon = ~long) %>%
  add_markers(text = ~paste(airport,
                            city,
                            state,
                            paste("Arrivals:", cnt),
                            sep = "<br />"),
              color = ~cnt,
              symbol = I("square"),
              size = I(8),
              hoverinfo = "text") %>%
  colorbar(title = "Incoming flights \nFebruary 2011") %>%
  layout(title = 'Most trafficked US airports \n(Hover for airport)',
         geo = g)
```

## Interactive worldwide airports

```{r, eval=TRUE}
g2 <- list(scope = 'world',
           showland = TRUE,
           landcolor = toRGB("gray95"))

plot_geo(airports, lat = ~Latitude, lon = ~Longitude) %>%
  add_markers(text = ~paste(AirportID, City, Country, sep = "<br />"),
              color = ~Country,
              symbol = I("circle"),
              size = I(3),
              hoverinfo = "text",
              colors = "Set1") %>%
  layout(title = 'Commercial Airports Worldwide',
         geo = g2)
```

Let's highlight the most important pieces of the code:

- With the `lat` and `lon` arguments, we provide information regarding the latitude and longitude of the airport's locations.
- With `add_markers()`, we can add trace(s) to a Plotly visualization.
- In `geo`, we set the reference between the provided geospatial coordinates and a geographic map (e.g. `usa`)
- In `layout()`, we modify the layout of a plotly visualization. For example, with title, we tell Plotly what `title` we want to appear above our plot.

---