---
title: "Python"
---

# Python in RStudio

The `knitr` package can execute a variety of [language chunks](http://rmarkdown.rstudio.com/authoring_knitr_engines.html#overview):

- Python, 
- SQL, and 
- Bash, among others.

For Python, instead of `{r}`, we begin the code chunk with `{python}`.

```{python}
x = 'hello, python world!'
print(x.split(' '))
```

Chunk options `echo` and `results` are all valid when using Python.

If the Python code generates raw HTML or LaTeX, the `results='asis'` option ensures that it is passed straight into the document’s output stream.

```{python, results='asis'}
def aucarre(x):
    print(x ** 2)
    
a = 3
aucarre(a)
```

By default, the interpreter returned by `Sys.which("python")` is used to execute the code. We can use a different python interpreter with `engine.path"/Users/me/anaconda/bin/python"` option.

```{python, engine.path="/home/ugo/anaconda3/bin/python3.5", eval=FALSE}
import sys
print(sys.version)
```

# Data exchange

Exchanging data between R chunks and Python chunks (and between Python chunks) is done via the file system. 

With data frames, we can use the `feather` package.

`feather`[^feather] transfer a data frame created with Pandas to R for plotting with `ggplot2`:

[^feather]: [A Fast On-Disk Format for Data Frames for R and Python, powered by Apache Arrow](https://blog.rstudio.com/2016/03/29/feather/).

```{r, include=FALSE, eval=FALSE}
head(mtcars, 3)
class(mtcars)

write.csv(mtcars, 'img/mtcars.csv')
```

Import the data with Python.

```{python, eval=FALSE}
import pandas
import feather

cars = pandas.read_csv("img/mtcars.csv")

feather.write_dataframe(cars, "img/cars.feather")
```

Read the feather file from R and plot the data frame using `ggplot2`.

```{r, include=FALSE}
library(feather)

write_feather(mtcars, 'img/cars.feather')
```

```{r}
library(feather)

mtcars2 <- read_feather("img/cars.feather")

head(mtcars2, 3)

library(ggplot2)

ggplot(mtcars2, aes(mpg, disp)) +
  geom_point() +
  geom_jitter()
```