---
title: "rbokeh"
---

# The `rbokeh` package

The [package](http://hafen.github.io/rbokeh/#background) and the Python library [website](http://bokeh.pydata.org/en/latest/). Bokeh graphing library runs in different languages (Python, Scala, Julia, R). We can plot all kinds of charts and some maps: the [gallery](https://bokeh.pydata.org/en/latest/docs/gallery.html).

# A quick example

With the `mtcars` dataset.

```{r}
library(rbokeh)

z <- lm(dist ~ speed, data = cars)

p <- figure(width = 600, height = 600) %>%
  ly_points(cars, hover = cars) %>%
  ly_lines(lowess(cars), legend = "lowess") %>%
  ly_abline(z, type = 2, legend = "lm")
p
```

# Scatter vs. `hexbin` plots

This is a dataset about 753 working women. 428 work outside the home, 325 don't. We remove observations where `hours` is zero. We also have socioeconomic factors affecting the work decision.

```{r, include=FALSE}
library(readxl)

# Read in the data set and assign to the object
work <- read_excel('data/Survival.xls', sheet = 'work')
str(work)
work$largecity <- as.factor(work$largecity)
work <- subset(work, work$hours != 0)
```

```{r}
p <- figure(width = 600, height = 600) %>%
  ly_points(faminc, hours, data = work, color = largecity, glyph = largecity,
    hover = list(faminc, hours, taxableinc, hfathereduc, hmothereduc, kids618, age))
p
```

```{r}
figure(width = 600, height = 600) %>%
  ly_hexbin(faminc, hours, data = work)
```

# Maps

`rbokeh` can work with map databases such as `maps` , `mapdata` (and `mapproj`). The only interactions are with the 'events' displayed on the map (points, bubbles, choropleth (fill)). However, for a fully interactive package: `leaflet`.

## Crude map of the world with capital cities

```{r}
library(maps)

data(world.cities)
caps <- subset(world.cities, capital == 1)
caps$population <- prettyNum(caps$pop, big.mark = ",")

figure(width = 800, height = 450, padding_factor = 0) %>%
  ly_map("world", col = "gray") %>%
  ly_points(long, lat, data = caps, size = 5, hover = c(name, country.etc, population))
```

## Maps of Canadian major CMAs

CMA: Census Metropolitan Area.

From `"world", "Canada"`.

```{r}
library(maps)
library(mapdata)

data(canada.cities)
metro <- subset(canada.cities, pop >= 1000000)
metro$population <- prettyNum(metro$pop, big.mark = ",")

figure(width = 800, height = 450, padding_factor = 0) %>%
  ly_map("world", "Canada", col = "lightgray") %>%
  ly_points(long, lat, data = metro, size = 10, color = 'red',
            hover = c(name, country.etc, population))
```

From `"worldHires", "Canada"`.

```{r}
library(maps)
library(mapdata)

figure(width = 800, height = 450, padding_factor = 0) %>%
  ly_map("worldHires", "Canada", col = "lightgray") %>%
  ly_points(long, lat, data = metro, size = 10, color = 'red',
            hover = c(name, country.etc, population))
```

## Spatial vectors

the `ly_polygons` function can hangle spatial vectors, but again, `rbokeh` should not be the first choice for plotting maps.

## Google Maps

The distribution of the Joshua Tree (hover of the points to see the pollinator).

```{r}
bkgd = read.csv('data/JoTrPresence02202008_dryad.csv')

gmap(lat = 35.75, lng = -116.25, zoom = 6, width = 700, height = 600) %>%
  ly_points(longitude, latitude, data = bkgd, alpha = 0.8, col = "red", hover = c(pollinator, longitude, latitude))
```

Nothing about OpenStreetMaps.

---